\vspace{-3em} \textbf{ Mapping stellar surfaces\\ I: Degeneracies in the rotational light curve problem }

### 2021-01-28 paper1/ms.tex
dan's comments

@@

While the stellar surfaces are all distinct, containing between one (top)
and six (bottom) large dark spots,
\textbf{their rotational light curves are identical}
(lower panel). This is true even in the absence of measurement
error: the mapping from a stellar surface
to its rotational light curve is so degenerate that there exist an infinite number of solutions
to the inverse problem. This fact has been pointed out recently in different contexts
\citep[e.g.,][]{Cowan2013,Luger2019,Basri2020}, but it dates back at least to
\citet{Russell1906}, who demonstrated it by expanding the surface
intensity of a celestial body in terms of spherical harmonics
(see Figure~\ref{fig:ylms}). \citet{Russell1906} showed
that many of the modes comprising the intensity profile of a spherical
object are in the \emph{null space}, the set of surface features that have identically
zero effect on the light curve. In fact, as we will show in \S\ref{sec:nullspace},
the \emph{vast majority} of the modes are in the null space for rotational
light curves of stars. This is what allows us to construct pathological
scenarios like that shown in Figure~\ref{fig:degeneracies}, where the light curve
could be explained by any number of spots atop a heterogeneous bright background.

@@

\subsection{Implications for inference}
%
The procedure we carried out in the previous section is similar to what was done in \citet{Rauscher2018}
for eclipse mapping of exoplanets. That work decomposed the surface map
using principal component analysis (PCA), finding an orthogonal set of
light curve signals and their corresponding surface modes (the left and right
singular vectors in SVD, respectively). Inference was then carried out in
the basis spanned by the components in the preimage, which can be uniquely
constrained by the data.

Let us therefore consider Figure~\ref{fig:nullspace_preimage} in the
context of an inference exercise. One can equivalently think of
the preimage as the solution to a least squares inference problem
in which a completely uninformative prior%
\footnote{%
    More specifically, a zero-mean, infinite variance Gaussian prior on the coefficients of $\mathbf{y}$.
}
is placed on the spherical harmonic
coefficients. In this case, the least squares solution is given by
%
\begin{proof}{test_svd_lstsq}
    \label{eq:inference}
    \hat{\mathbf{y}}
    &=
    \lim_{\lambda \rightarrow 0} \left( \pmb{\mathcal{A}}^\top \pmb{\mathcal{A}} + \lambda \mathbf{I}\right)^{-1} \pmb{\mathcal{A}}^\top (\mathbf{f} - \mathbf{1})
    \nonumber\\
    &= \mathbf{y}_\bullet
    \quad.
\end{proof}
%
In this sense, $\mathbf{y}_\bullet$ represents our knowledge about the
surface of a star after an observation if we have no prior information
whatsoever on $\mathbf{y}$.
\emph{Any other information about the surface must come from the prior.}%

@@

To better understand this effect, let us
define the \emph{posterior shrinkage} $S$ as
%
\begin{align}
    \label{eq:shrinkage}
    S \equiv 1 - \lim\limits_{\sigma_0^2 \rightarrow \infty}
    \frac{\sigma^2}{\sigma_0^2}
    \quad,
\end{align}
%
where $\sigma_0^2$ is the prior variance
and $\sigma^2$ is the posterior variance
on a particular surface mode we are trying to constrain
\citep[see, e.g.,][]{Betancourt2018}.
The posterior shrinkage is a measure of how informative a measurement is about a
given mode on the surface in the limit of infinite signal-to-noise ratio (SNR)
and is independent of what the stellar surface actually looks like.
If, at infinite SNR and with a completely uninformative prior,
a particular mode can be learned exactly from a dataset, the posterior
shrinkage is defined to be unity. Conversely, if the data is completely
unconstraining of that mode (i.e., it is entirely in the null space),
$S$ will tend to zero.

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/nullspace_ensemble_single.pdf}
        \oscaption{nullspace_ensemble_single}{%
            Posterior shrinkage as a function of spherical harmonic
            degree $l$ given a single observation of a star at a random
            inclination (thin blue curves). The mean shrinkage is shown
            as the thicker curve. The information content of light curves
            tends to zero as $l$ increases, and odd $l > 1$ modes are in the
            null space at all inclinations.
            \label{fig:nullspace_ensemble_single}
        }
    \end{centering}
\end{figure}

Figure~\ref{fig:nullspace_ensemble_single} shows the posterior shrinkage
given a single observation of a star at a random inclination.
Each thin blue curve corresponds to a particular draw from an isotropic
inclination distribution; the thick blue curve is the average over 300 trials.
For some of the low-degree modes, the shrinkage is relatively high: it is
fairly easy to constrain the dipole moment from a light curve, as this is
usually the dominant sinusoidal signal. However, as the degree $l$
increases, the shrinkage decreases dramatically: at $l = 14$, corresponding
to features on scales of roughly $13^\circ$, the light curve
can only tell us about $\sim 10\%$ of the total information about what the
surface looks like. As $l$ increases further, $S$ tends to zero.
Another important feature of the shrinkage, which we hinted at above,
is that it is exactly zero for
all odd-degree modes above $l = 1$. This is a well-known fact: all odd spherical
harmonics other than the dipole are in the null space \emph{regardless of
    inclination} \citep[e.g.,][]{Luger2019}. In other words, these spherical
harmonics are perfectly antisymmetric in projection over the unit disk
when viewed from any orientation. Absent structure to break these symmetries
(see below), we simply cannot learn anything about these modes from
stellar light curves. If we average over the shrinkage for all modes up to $l=15$,
we find that a single light curve measurement can only tell us $\sim 9\%$
of the information about the surface on those scales.

Fortunately, however, there is quite a bit of variance in the shrinkage
for different values of the stellar inclination.
As we will see, we can use this dependence of the null space on inclination to our
advantage. If we could observe a star from many different vantage points,
we would be able to break many of the degeneracies at play, since we
would get different constraints on the amplitude of each mode when viewed
at different inclinations. This, of course, is not possible (at least not
yet!). But what we \emph{can} do is observe many similar stars, each viewed
at a different (random) inclination, and attempt to learn something about
the properties of the ensemble of stars as a whole.
In the
following section, we explore the role of ensemble analyses in breaking
the degeneracies of the mapping problem in more detail.

@@

In an ensemble analysis, we assume we observe the lightcurves of many stars
that are ``similar'' in some statistical sense. As a thought experiment,
let us consider an extreme version of ensemble analysis in which all the
stars in our sample happen to have \emph{identical} surfaces. We will
still assume they are oriented at random inclinations, as we would expect for
field stars.
%
Figure~\ref{fig:nullspace_ensemble} shows the posterior shrinkage
curves for this hypothetical scenario, assuming we have access to
light curves of 1 (blue), 3 (orange), 10 (green) and 30 (red)
identical stars viewed at random inclinations.

@@

The addition of light curve measurements at different orientations
increases the posterior shrinkage at all even spherical harmonic degrees
(the odd degrees, as we mentioned above, are always invisible).
Note that since we are in the limit of infinite SNR, the fact that we have
more light curves (i.e., more data) is irrelevant: the
increase in the shrinkage is instead due to the fact that our observations
from different vantage points broke some degeneracies in the problem.
This is a consequence of the fact we mentioned in the previous section:
the null space (for the even modes)
is a strong function of the inclination.

If we average over all modes, we obtain a total shrinkage of $\sim 24\%$
for $l\leq15$ when our sample size is 3 (orange curves): we have more than doubled the
information content of our observations. If we further increase our sample size
to 10 (green curves), the posterior shrinkage approaches $100\%$ for all even $l\leq15$
modes, effectively saturating for a sample size of 30 (red curves).
Thus, if we were able to measure light curves of identical stars
from many different inclinations, the null space would consist \emph{only}
of the odd modes. In the limit of a large number of light curves,
and assuming all stars in the sample have identical surfaces,
\textbf{ensemble analyses can tell us up to
    half of all the information about the stellar surfaces.}

@@

To understand how limb darkening affects our ability to infer
surface properties from stellar light curves,
let us repeat the experiment from the previous section,
this time with moderate quadratic limb darkening (with coefficients
$u_1 = 0.5$ and $u_2 = 0.25$, although our conclusions do not
qualitatively change for different values).
The top panel of Figure~\ref{fig:nullspace_ensemble_ld} shows the
posterior shrinkage plot (same as Figure~\ref{fig:nullspace_ensemble}, but
this time accounting for limb darkening). Interestingly, there is no longer a clean division of
the null space between even and odd modes in the limit of a large number
of light curves.
This is because limb darkening effectively lifts odd modes out of the null space, \emph{at the
    expense of the even modes}. While no coefficient lies entirely in the
null space ($S = 0$) when limb darkening is present, no coefficient
can be uniquely inferred ($S = 1$), either. This can be understood by noting that
a polynomial limb darkening law can be written
exactly as a linear combination of the $m=0$ spherical harmonics
up to a degree equal to the order of the limb darkening
\citep[in this case, $l = 2$;]{Luger2019,Agol2020}.
Since the limb darkening operation is a (multiplicative) downweighting of
the surface intensity, the map seen by the observer is just the product
of the spherical harmonic representation of the surface ($\mathbf{y}$)
and the spherical harmonic representation of the limb darkening profile.
And since spherical harmonics are just polynomials on the surface of the sphere,
the product of spherical harmonics of degree $l_1$ and $l_2$ is a spherical
harmonic of degree $l_1 + l_2$. This means that the linear limb darkening
component ($l = 1$) effectively raises the degree of all spherical harmonic
coefficients of the surface map by one. This has the effect of reversing
the null space: under \emph{only} linear limb darkening, it is the \emph{even}
modes that would be in the null space. However, the quadratic
limb darkening term ($l = 2$) raises the degree of all spherical harmonics by two,
so its presence ensures that the even modes can still be probed to some extent.
In reality, the true limb darkening profile of a stellar surface is more
complicated than a two-parameter quadratic model can capture; but one may still
expand it as an arbitrary order polynomial, in which case the argument still
applies---limb darkening mixes the null space and the preimage in a nontrivial
way.
%
The fact that no coefficient can be determined uniquely---i.e., there are
perfect degeneracies involving \emph{all} modes on the surface---could make it more
difficult in practice to perform ensemble analyses on limb-darkened stars.

@@

In reality, it is unlikely that all stars in a given ensemble will have exactly
the same limb darkening coefficients, however ``similar'' the stars may be.
Figure~\ref{fig:nullspace_ensemble_ld_var} shows the same
posterior shrinkage plot as Figure~\ref{fig:nullspace_ensemble_ld},
but for the case where each star has coefficients
$u_1 = 0.5 \pm 0.05$ and $u_2 = 0.25 \pm 0.025$; i.e., we add a scatter of
10\% in the value of these coefficients. The plot shows the posterior
shrinkage in the hypothetical case where we know the coefficients for
each star exactly. Now, as the size of the ensemble increases, the posterior
shrinkage approaches unity \emph{for all spherical harmonic modes}.
In the same way that the null space is a strong function of the inclination,
allowing us to chip away at it with observations at different inclinations,
the null space is also a strong function of the limb darkening law. Even a
small amount of variance in the coefficients is sufficient to constrain all surface
modes exactly (in the limit of infinite SNR and a large number of light curves).

@@

There are several simplifying assumptions we made in this paper that
are worth discussing. First, in our characterization of the null space
we assumed we knew the stellar inclination, the stellar rotation period,
and the limb darkening coefficients
exactly, and we computed the information content of stellar light curves
in the limit of infinite SNR. None of these assumptions are valid in
practice. In realistic scenarios, the posterior shrinkage will be
necessarily \emph{lower} than what we presented here: the curves in
Figure~\ref{fig:nullspace_ensemble}, for instance, are therefore
strict upper bounds on the amount of information that can be learned about
the surface. In some cases, it may be possible to infer the inclination
from spectroscopic $v \sin I$ measurements, or the limb darkening coefficients
from the shape of transiting exoplanet light curves; but any uncertainty
in these quantities will degrade our ability to constrain
information about the surface.

>>>>

\newcommand{\shrinkage}{{variance reduction\,}}

@@

While the stellar surfaces are all distinct, containing between one (top)
and six (bottom) large dark spots,
\textbf{their rotational light curves are identical}
(lower panel). This is true even in the absence of measurement
error: the mapping from a stellar surface
to its rotational light curve is so degenerate that there exist an infinite number of solutions
to the inverse problem. This fact has been pointed out recently in different contexts
\citep[e.g.,][]{Cowan2013,Rauscher2018,Luger2019,Basri2020}, but it dates back at least to
\citet{Russell1906}, who demonstrated it by expanding the surface
intensity of a celestial body in terms of spherical harmonics
(see Figure~\ref{fig:ylms}). \citet{Russell1906} showed
that many of the modes comprising the intensity profile of a spherical
object are in the \emph{null space}, the set of surface features that have identically
zero effect on the light curve. In fact, as we will show in \S\ref{sec:nullspace},
the \emph{vast majority} of the modes are in the null space for rotational
light curves of stars. This is what allows us to construct pathological
scenarios like that shown in Figure~\ref{fig:degeneracies}, where the light curve
could be explained by any number of spots atop a heterogeneous bright background.

@@

\subsection{Implications for inference}
%
The model mapping spherical harmonic coefficients to observed fluxes described
in the preceding sections is linear, so we might expect that we could fit
for the spherical harmonics using linear least-squares
%
\begin{align}
    \label{eq:linlstsq}
    \hat{\mathbf{y}} & \stackrel{?}{=}
    \left(\pmb{\mathcal{A}}^\top\,\pmb{\mathcal{A}}\right)^{-1}\,\pmb{\mathcal{A}}^\top\,\left(\mathbf{f} - \mathbf{1}\right)
    \quad.
\end{align}
%
But, since the flux operator $\pmb{\mathcal{A}}$ is low-rank, the model is
underdetermined, so the above operation is not defined and, equivalently,
the Fisher information matrix
%
\begin{align}
    \label{eq:fisher-info}
    \pmb{\mathcal{I}}(\mathbf{y}) & = \frac{1}{\sigma_f^2} \, \pmb{\mathcal{A}}^\top\,\pmb{\mathcal{A}}
\end{align}
%
is singular.
In Equation~(\ref{eq:fisher-info}), $\sigma_f$ is the flux measurement uncertainty.
There exist many methods and procedures for linear regression for underdetermined
models, but all solutions amount to imposing stronger assumptions about the
model in order to break the degeneracies.

One standard method is regularized least squares, in which
Equation~(\ref{eq:linlstsq}) becomes
%
\begin{align}
    \hat{\mathbf{y}}_\lambda & \equiv
    \left(\pmb{\mathcal{A}}^\top\,\pmb{\mathcal{A}} + \lambda\,\mathbf{I}\right)^{-1}\,\pmb{\mathcal{A}}^\top\,\left(\mathbf{f} - \mathbf{1}\right)
\end{align}
%
where $\mathbf{I}$ is the identity matrix and $\lambda$ is a parameter
controlling the strength of the regularization.
In a Bayesian context, this can be interpreted as placing a Gaussian prior
with variance $\sigma_0^{2} = \nicefrac{\sigma_f^2}{\lambda}$ on the spherical harmonic coefficients.

In the limit of infinitesimal regularization, it can be demonstrated
\citep[see][for example]{Hogg2021} that
%
\begin{proof}{test_svd_lstsq}
    \label{eq:inference}
    \lim_{\lambda \rightarrow 0_+} \hat{\mathbf{y}}_\lambda
    % &=
    % \lim_{\lambda \rightarrow 0} \left( \pmb{\mathcal{A}}^\top \pmb{\mathcal{A}} + \lambda \mathbf{I}\right)^{-1} \pmb{\mathcal{A}}^\top (\mathbf{f} - \mathbf{1})
    % \nonumber\\
    &= \mathbf{y}_\bullet
    \quad.
\end{proof}
%
In this sense, $\mathbf{y}_\bullet$ represents our knowledge about the
surface of a star after an observation if we have no prior information
whatsoever on $\mathbf{y}$.
\emph{Any other information about the surface is entirely driven by our assumptions.}%

% It is interesting to quantify the information content of a light curve as a
% function of spherical harmonic coefficients.
% While Equation~(\ref{eq:fisher-info}) provides a compact expression for the
% Fisher information matrix, the most important feature that we want to quantify
% is the covariance between coefficients.
% This is most naturally captured by the covariance matrix of the likelihood
% function for the spherical harmonic coefficients:
% %
% \begin{align}
%     \pmb{\Sigma}_\lambda & =
%     \sigma^2\,\left(\pmb{\mathcal{A}}^\top\,\pmb{\mathcal{A}} + \lambda\,\mathbf{I}\right)^{-1} \quad.
% \end{align}
% %
% Below, we use this to quantify the width of the likelihood for each spherical
% harmonic coefficient by plotting the ``relative variance'' $S$, which we define
% as the diagonal of the matrix $\pmb{\Sigma}_\lambda$ in units of
% $\lambda / \sigma^2$ in the limit where $\lambda \to 0_+$.
% This choice of units constrains $0 \le S \le 1$ and allows easy comparisons
% between the information content of different datasets without being sensitive
% to the specific modeling assumptions.
% Under this definition, when $S$ approaches one for a particular coefficient,
% this means that the likelihood function provides no information about that
% coefficient, while $S = 0$ indicates that that coefficient can be perfectly measured.

% This relative variance $S$ can be interpreted either as the Cram\'er--Rao
% lower bound on the variance of an estimator for a spherical harmonic
% \citep[e.g.,][]{Li2012}, although our specific choice of units are somewhat
% non-standard.
% Similarly, in a Bayesian context, this is the ``posterior shrinkage'', the
% ratio of the posterior variance to the prior variance in the limit of
% infinite prior variance \citep[e.g.,][]{Betancourt2018}.

@@

To better understand this effect, let us define the quantity
%
\begin{align}
    S \equiv
    1 -
    \lim_{\lambda \rightarrow 0_+}
    \mathrm{diag}
    \left(
    \lambda
    \left(\pmb{\mathcal{A}}^\top\,\pmb{\mathcal{A}} + \lambda\,\mathbf{I}\right)^{-1}
    \right)
    \quad,
\end{align}
%
which we will refer to as the \emph{\shrinkage}
of the coefficients $\mathbf{y}$ characterizing the stellar surface.
Note that in a Bayesian context, this is
equivalent to the \emph{posterior shrinkage}
%
\begin{align}
    \label{eq:shrinkage}
    S = 1 - \lim\limits_{\sigma_0^2 \rightarrow \infty}
    \frac{\sigma^2}{\sigma_0^2}
    \quad,
\end{align}
%
where $\sigma_0^2$ is the prior variance
and $\sigma^2$ is the posterior variance
on a particular surface mode we are trying to constrain
\citep[see, e.g.,][]{Betancourt2018}.

The \shrinkage is a dimensionless quantity describing how informative a measurement is about a
given mode on the surface in the limit of infinite signal-to-noise ratio (SNR)
and is independent of what the stellar surface actually looks like.
If, at infinite SNR and with no regularization
(or, in a Bayesian context, a completely uninformative prior),
a particular mode can be learned exactly from a dataset, the \shrinkage
is defined to be unity. Conversely, if the data is completely
unconstraining of that mode (i.e., it is entirely in the null space),
$S$ will tend to zero.

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/nullspace_ensemble_single.pdf}
        \oscaption{nullspace_ensemble_single}{%
            The \shrinkage as a function of spherical harmonic
            degree $l$ given a single observation of a star at a random
            inclination (thin blue curves). The mean \shrinkage is shown
            as the thicker curve. The information content of light curves
            tends to zero as $l$ increases, and odd $l > 1$ modes are in the
            null space at all inclinations.
            \label{fig:nullspace_ensemble_single}
        }
    \end{centering}
\end{figure}

Figure~\ref{fig:nullspace_ensemble_single} shows the \shrinkage $S$
given a single observation of a star at a random inclination.
Each thin blue curve corresponds to a particular draw from an isotropic
inclination distribution; the thick blue curve is the average over 300 trials.
For some of the low-degree modes, $S$ is relatively high: it is
fairly easy to constrain the dipole moment from a light curve, as this is
usually the dominant sinusoidal signal. However, as the degree $l$
increases, $S$ decreases dramatically: at $l = 14$, corresponding
to features on scales of roughly $13^\circ$, the light curve
can only tell us about $\sim 10\%$ of the total information about what the
surface looks like. As $l$ increases further, $S$ tends to zero.
Another important feature of $S$, which we hinted at above,
is that it is exactly zero for
all odd-degree modes above $l = 1$. This is a well-known fact: all odd spherical
harmonics other than the dipole are in the null space \emph{regardless of
    inclination} \citep[e.g.,][]{Luger2019}. In other words, these spherical
harmonics are perfectly antisymmetric in projection over the unit disk
when viewed from any orientation. Absent structure to break these symmetries
(see below), we simply cannot learn anything about these modes from
stellar light curves. If we average over $S$ for all modes up to $l=15$,
we find that a single light curve measurement can only tell us $\sim 9\%$
of the information about the surface on those scales.

Fortunately, however, there is quite a bit of scatter in $S$
for different values of the stellar inclination.
As we will see, we can use this dependence of the null space on inclination to our
advantage. If we could observe a star from many different vantage points,
we would be able to break many of the degeneracies at play, since we
would get different constraints on the amplitude of each mode when viewed
at different inclinations. This, of course, is not possible (at least not
yet!). But what we \emph{can} do is observe many similar stars, each viewed
at a different (random) inclination, and attempt to learn something about
the properties of the ensemble of stars as a whole.
In the
following section, we explore the role of ensemble analyses in breaking
the degeneracies of the mapping problem in more detail.

@@

In an ensemble analysis, we assume we observe the lightcurves of many stars
that are ``similar'' in some statistical sense. As a thought experiment,
let us consider an extreme version of ensemble analysis in which all the
stars in our sample happen to have \emph{identical} surfaces. We will
still assume they are oriented at random inclinations, as we would expect for
field stars.
%
Figure~\ref{fig:nullspace_ensemble} shows the \shrinkage
curves for this hypothetical scenario, assuming we have access to
light curves of 1 (blue), 3 (orange), 10 (green) and 30 (red)
identical stars viewed at random inclinations.

@@

The addition of light curve measurements at different orientations
increases the \shrinkage at all even spherical harmonic degrees
(the odd degrees, as we mentioned above, are always invisible).
Note that since we are in the limit of infinite SNR, the fact that we have
more light curves (i.e., more data) is irrelevant: the
increase in the \shrinkage is instead due to the fact that our observations
from different vantage points broke some degeneracies in the problem.
This is a consequence of the fact we mentioned in the previous section:
the null space (for the even modes)
is a strong function of the inclination.

If we average over all modes, we obtain an average $S$ of $\sim 24\%$
for $l\leq15$ when our sample size is 3 (orange curves): we have more than doubled the
information content of our observations. If we further increase our sample size
to 10 (green curves), the \shrinkage approaches $100\%$ for all even $l\leq15$
modes, effectively saturating for a sample size of 30 (red curves).
Thus, if we were able to measure light curves of identical stars
from many different inclinations, the null space would consist \emph{only}
of the odd modes. In the limit of a large number of light curves,
and assuming all stars in the sample have identical surfaces,
\textbf{ensemble analyses can tell us up to
    half of all the information about the stellar surfaces.}

@@

To understand how limb darkening affects our ability to infer
surface properties from stellar light curves,
let us repeat the experiment from the previous section,
this time with moderate quadratic limb darkening (with coefficients
$u_1 = 0.5$ and $u_2 = 0.25$, although our conclusions do not
qualitatively change for different values).
The top panel of Figure~\ref{fig:nullspace_ensemble_ld} shows the
\shrinkage plot (same as Figure~\ref{fig:nullspace_ensemble}, but
this time accounting for limb darkening). Interestingly, there is no longer a clean division of
the null space between even and odd modes in the limit of a large number
of light curves.
This is because limb darkening effectively lifts odd modes out of the null space, \emph{at the
    expense of the even modes}. While no coefficient lies entirely in the
null space ($S = 0$) when limb darkening is present, no coefficient
can be uniquely inferred ($S = 1$), either. This can be understood by noting that
a polynomial limb darkening law can be written
exactly as a linear combination of the $m=0$ spherical harmonics
up to a degree equal to the order of the limb darkening
\citep[in this case, $l = 2$;]{Luger2019,Agol2020}.
Since the limb darkening operation is a (multiplicative) downweighting of
the surface intensity, the map seen by the observer is just the product
of the spherical harmonic representation of the surface ($\mathbf{y}$)
and the spherical harmonic representation of the limb darkening profile.
And since spherical harmonics are just polynomials on the surface of the sphere,
the product of spherical harmonics of degree $l_1$ and $l_2$ is a spherical
harmonic of degree $l_1 + l_2$. This means that the linear limb darkening
component ($l = 1$) effectively raises the degree of all spherical harmonic
coefficients of the surface map by one. This has the effect of reversing
the null space: under \emph{only} linear limb darkening, it is the \emph{even}
modes that would be in the null space. However, the quadratic
limb darkening term ($l = 2$) raises the degree of all spherical harmonics by two,
so its presence ensures that the even modes can still be probed to some extent.
In reality, the true limb darkening profile of a stellar surface is more
complicated than a two-parameter quadratic model can capture; but one may still
expand it as an arbitrary order polynomial, in which case the argument still
applies---limb darkening mixes the null space and the preimage in a nontrivial
way.
%
The fact that no coefficient can be determined uniquely---i.e., there are
perfect degeneracies involving \emph{all} modes on the surface---could make it more
difficult in practice to perform ensemble analyses on limb-darkened stars.

@@

In reality, it is unlikely that all stars in a given ensemble will have exactly
the same limb darkening coefficients, however ``similar'' the stars may be.
Figure~\ref{fig:nullspace_ensemble_ld_var} shows the same
\shrinkage plot as Figure~\ref{fig:nullspace_ensemble_ld},
but for the case where each star has coefficients
$u_1 = 0.5 \pm 0.05$ and $u_2 = 0.25 \pm 0.025$; i.e., we add a scatter of
10\% in the value of these coefficients. The plot shows the \shrinkage
in the hypothetical case where we know the coefficients for
each star exactly. Now, as the size of the ensemble increases, the \shrinkage
approaches unity \emph{for all spherical harmonic modes}.
In the same way that the null space is a strong function of the inclination,
allowing us to chip away at it with observations at different inclinations,
the null space is also a strong function of the limb darkening law. Even a
small amount of variance in the coefficients is sufficient to constrain all surface
modes exactly (in the limit of infinite SNR and a large number of light curves).

@@

There are several simplifying assumptions we made in this paper that
are worth discussing. First, in our characterization of the null space
we assumed we knew the stellar inclination, the stellar rotation period,
and the limb darkening coefficients
exactly, and we computed the information content of stellar light curves
in the limit of infinite SNR. None of these assumptions are valid in
practice. In realistic scenarios, the \shrinkage will be
necessarily \emph{lower} than what we presented here: the curves in
Figure~\ref{fig:nullspace_ensemble}, for instance, are therefore
strict upper bounds on the amount of information that can be learned about
the surface. In some cases, it may be possible to infer the inclination
from spectroscopic $v \sin I$ measurements, or the limb darkening coefficients
from the shape of transiting exoplanet light curves; but any uncertainty
in these quantities will degrade our ability to constrain
information about the surface.
